A reproducible framework for undergraduate data science research

### 2019-12-05 Rmd/methods.Rmd
updated & organized Methods

computational topics: LDA & topic modeling; time series analysis; sentiment analysis.

@@

Our framework for mentored student research projects involves these components:

@@

>>>>

@@

@@

With the goal of promoting transparency in our research, we encouraged students to 
use `git` for version control of their code and documents and to share their code via
the website Github (https://github.com). One student also enrolled in Karl Broman's class on 
tools for reproducible research. This class features `git` and Github throughout its lectures 
and activities.
